A Dynamic Intrafamily Model of Child Behavior Problems and Birth Timing

### 2018-09-12 inst/paper/paper.Rmd
Teak
Multigroup Stuff

library(birthtiming) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
```

@@

```{r resultsdata, include=FALSE}
child_difficulty <- load_and_format_NLSY()
naive_tidy <- run_naive_sem()
load("../data/derived_data/naive_tidy.RData")
load("../data/derived_data/child_difficulty.RData")
```

@@

Some additional results notes:
1. Parity significantly predicts higher child difficulty (0.161, t=5.54). Inclusion has no effect on mother's age effects.
2. Early child health problems do not predict child difficulty or impact mother's age effects.
3. At-birth characteristics (e.g. birth weight, gestation time) do not have substantively strong effects or impacts on mother's age effects.

>>>>

# library(birthtiming) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
```

@@

```{r resultsdata, include=FALSE}
# child_difficulty <- load_and_format_NLSY()
# naive_tidy <- run_naive_sem()
load("../data/derived_data/naive_tidy.RData")
load("../data/derived_data/child_difficulty.RData")
```

@@

Some additional results notes:

1. Parity significantly predicts higher child difficulty (0.161, t=5.54). Inclusion has no effect on mother's age effects.
2. Early child health problems do not predict child difficulty or impact mother's age effects.
3. At-birth characteristics (e.g. birth weight, gestation time) do not have substantively strong effects or impacts on mother's age effects.
